---
title: "Test analysis"
author: "Daniel Kassler"
date: "November 30, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "~/Research/ldreg")
knitr::opts_chunk$set(echo = F, warning = F)
```

```{r}
library(ggplot2)
```


Unless otherwise specified, $M = N1 = N2 = N_{ref} = 10,000$ and $N_{shared} = 3,000$. SNPs are randomly assigned into groups $2$ and $3$, comprising $25\%$ and $40\%$ of the total number of SNPs respectively; group $1$ consists of all SNPs. Jackknife estimation is performed with 200 blocks.

#Null Test

```{r, warning = F, include = F}
library(foreach)
library(dplyr)

jack <- foreach(wt = c("jack", "jack_wt"), .combine = bind_rows) %:%
  foreach(i = 1:100, .combine = bind_rows, .errorhandling = "remove") %do% {
    jack <- readRDS(sprintf("Output/test_null/2016-11-30/out/%s.%s.rds", wt, i))
    jack %>% 
      as.data.frame() %>% 
      tibble::rownames_to_column(var = "group") %>% 
      tidyr::gather("var", "value", -group) %>% 
      mutate(index = i, wt = (wt == "jack_wt"))
  }
```

```{r, results = 'asis'}
jack %>% 
  tidyr::spread(var, value) %>% 
  mutate(cover_zero = (estim - 2*se < 0) & (estim + 2*se > 0),
         group = tidyr::extract_numeric(group)) %>% 
  group_by(wt, group) %>% 
  summarize(
    "CI Cov 0" = scales::percent(mean(cover_zero)),
    "Avg J.Est" = mean(estim),
    "Avg Est" = mean(upsilon_hat),
    "Avg J.SE" = mean(se),
    "SD J.Est" = sd(estim),
    "SD Est" = sd(upsilon_hat)
  ) %>% 
  {knitr::kable(.)}
  #{print(xtable::xtable(., ""), type = "html")}
```

```{r}
ggplot(data = jack %>% 
         tidyr::spread(var, value)) +
  geom_density(aes(x = upsilon_hat, color = group, linetype = wt)) + 
  theme_bw() +
  labs(x = "Estimated Upsilon", title = "Density Plot of Estimates")
```


#Non-Null Test

```{r}
true_upsilon <- c(-2.84507392318969e-05, -3.35384263223196e-05, 4.43856550207098e-05)

```

```{r, eval = T}
.tmp <- foreach(wt = c("nowt", "wt"), .combine = bind_rows) %:%
  foreach(i = 1:100, .combine = bind_rows, .errorhandling = "remove") %do% {
    jack <- readRDS(sprintf("Output/pass_true_r_non_null/2016-11-30b/out/jack.%s.emp.%s.rds", wt, i))
    jack %>% 
      as.data.frame() %>% 
      tibble::rownames_to_column(var = "group") %>% 
      tidyr::gather("var", "value", -group) %>% 
      mutate(index = i, wt = (wt == "wt"))
  } %>% 
  mutate(group = tidyr::extract_numeric(group),
         true_val = true_upsilon[group])
.tmp %>%
  tidyr::spread(var, value) %>% 
  mutate(cover_zero = (estim - 2*se < 0) & (estim + 2*se > 0),
         cover_true = (estim - 2*se < true_val) & (estim + 2*se > true_val),
         group = tidyr::extract_numeric(group)) %>% 
  group_by(wt, group) %>% 
  summarize(
    "CI Cov 0" = scales::percent(mean(cover_zero)),
    "CI Cov True" = scales::percent(mean(cover_true)),
    "Avg J.Est" = mean(estim),
    "Avg Est" = mean(upsilon_hat),
    "J.Bias" = mean(estim - true_val),
    "Bias" = mean(upsilon_hat - true_val),
    "Avg J.SE" = mean(se),
    "SD J.Est" = sd(estim),
    "SD Est" = sd(upsilon_hat)
  ) %>% 
  {knitr::kable(.)}
  #{print(xtable::xtable(., ""), type = "html")}
```

In the plot below, the vertical lines indicate the true (non-null) values of $\upsilon$ for each group.

```{r, eval = T}
ggplot(data = .tmp %>% 
         tidyr::spread(var, value)) +
  geom_density(aes(x = upsilon_hat, color = factor(group), linetype = wt)) +
  geom_vline(aes(xintercept = true_val, color = factor(group))) +
  theme_bw() +
  labs(x = "Estimated Upsilon", title = "Density Plot of Estimates")
  
```

#Comparison to True $r$ Matrix

Are the issues we see the result of a poorly estimated $r$ matrix? To check this, compare the results from simulations where $r$ is estimated from a reference population to the results from the same simulations, but using the true $r$ (without bias correction) instead of a bias corrected estimate.

##Null Case

```{r, eval = T}
.tmp <- foreach(r = c("emp", "true"), .combine = bind_rows) %:%
  foreach(wt = c("nowt", "wt"), .combine = bind_rows) %:%
  foreach(i = 1:100, .combine = bind_rows, .errorhandling = "remove") %do% {
    jack <- readRDS(sprintf("Output/pass_true_r_null/2016-11-30d/out/jack.%s.%s.%s.rds", wt, r, i))
    jack %>% 
      as.data.frame() %>% 
      tibble::rownames_to_column(var = "group") %>% 
      tidyr::gather("var", "value", -group) %>% 
      mutate(index = i, wt = (wt == "wt"), r = r)
  }
.tmp %>% 
  tidyr::spread(var, value) %>% 
  mutate(cover_zero = (estim - 2*se < 0) & (estim + 2*se > 0),
         group = tidyr::extract_numeric(group)) %>% 
  group_by(wt, group, r) %>% 
  summarize(
    "CI Cov 0" = scales::percent(mean(cover_zero)),
    "Avg J.Est" = mean(estim),
    "Avg Est" = mean(upsilon_hat),
    "Avg J.SE" = mean(se),
    "SD J.Est" = sd(estim),
    "SD Est" = sd(upsilon_hat)
  ) %>% 
  {knitr::kable(.)}
  #{print(xtable::xtable(., ""), type = "html")}
```

##Non-Null Case

```{r}

```


```{r, eval = T}
.tmp <- foreach(r = c("emp", "true"), .combine = bind_rows) %:%
  foreach(wt = c("nowt", "wt"), .combine = bind_rows) %:%
  foreach(i = 1:100, .combine = bind_rows, .errorhandling = "remove") %do% {
    jack <- readRDS(sprintf("Output/pass_true_r_non_null/2016-11-30b/out/jack.%s.%s.%s.rds", wt, r, i))
    jack %>% 
      as.data.frame() %>% 
      tibble::rownames_to_column(var = "group") %>% 
      tidyr::gather("var", "value", -group) %>% 
      mutate(index = i, wt = (wt == "wt"), r = r)
  } %>% 
  mutate(group = tidyr::extract_numeric(group),
         true_val = true_upsilon[group])
.tmp %>%
  tidyr::spread(var, value) %>% 
  mutate(cover_zero = (estim - 2*se < 0) & (estim + 2*se > 0),
         cover_true = (estim - 2*se < true_val) & (estim + 2*se > true_val),
         group = tidyr::extract_numeric(group)) %>% 
  group_by(wt, r, group) %>% 
  summarize(
    "CI Cov 0" = scales::percent(mean(cover_zero)),
    "CI Cov True" = scales::percent(mean(cover_true)),
    "Avg J.Est" = mean(estim),
    "Avg Est" = mean(upsilon_hat),
    "J.Bias" = mean(estim - true_val),
    "Bias" = mean(upsilon_hat - true_val),
    "Avg J.SE" = mean(se),
    "SD J.Est" = sd(estim),
    "SD Est" = sd(upsilon_hat)
  ) %>% 
  {knitr::kable(.)}
```

#LD Score Comparison

Here we aggregate the true LD scores and bias corrected empirical LD scores for 100 random simulations of the sort used in the other simulation analyses here, and compare them to see if there is systematic mis-estimation.

```{r}
ld_compare <- readRDS("Save/ld_compare.all.rds")
ld_compare %>% 
  lapply(as.data.frame) %>% 
  bind_rows(.id = "trial") %>%
  tidyr::extract(trial, "trial", "\\w+\\.(\\d+)\\.\\w+", convert = TRUE) %>% 
  filter(trial <= 1) %>% 
  {
    ggplot(data = ., aes(x = ld_true, y = ld_bias)) +
      geom_point(alpha = 0.05, position = position_jitter(height = 0, width = 0.4)) +
      geom_abline(color = "red") +
      theme_bw() +
      labs(x = "True LD Scores", y = "Bias Corrected Empirical LD Scores",
           title = "LD Score Comparison for 1 Run")
  }

ld_compare %>% 
  lapply(as.data.frame) %>% 
  bind_rows(.id = "trial") %>%
  tidyr::extract(trial, "trial", "\\w+\\.(\\d+)\\.\\w+", convert = TRUE) %>% 
  filter(trial <= 100) %>% 
  {
    ggplot(data = ., aes(x = ld_true, y = ld_bias)) +
      geom_point(alpha = 0.01, position = position_jitter(height = 0, width = 0.4)) +
      geom_abline(color = "red") +
      theme_bw() +
      labs(x = "True LD Scores", y = "Bias Corrected Empirical LD Scores",
           title = "LD Score Comparison for 100 Runs")
  }
```

